\documentclass{nordic}
\usepackage[utf8]{inputenc} % In case one needs to specify character encoding
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\newcommand{\NSCM}{23}
\newcommand{\submissionyear}{2010}
\newcommand{\submissiondate}{September 15th 2010}
\newcommand{\submissionpage}{http://congress.cimne.upc.es/nscm-\NSCM/frontal}

\header{
  \NSCM rd Nordic Seminar on Computational Mechanics\\
  NSCM-\NSCM\\
  A. Eriksson and G. Tibert (Eds)\\
  \copyright KTH, Stockholm, \submissionyear
}

\title{Multiscale Modeling of Sintering of Hard Metals}

\author{Mikael Öhman$^*$, Kenneth Runesson and Fredrik Larsson}

\heading{Mikael Öhman, Kenneth Runesson and Fredrik Larsson}

\address{%
Department of Applied Mechanics\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
e-mail: \url{mikael.ohman@chalmers.se}, web page: \url{http://www.chalmers.se/am/EN/}
}

\keywords{Sintering, Sintering stress, Surface tension, Homogenization, FE$^2$}

\abstract{%
In this contribution, we discuss the multiscale modeling of sintering of hard metal, which is composed of hard particles (WC) with a melted binder (Co).
The sintering phenomenon on the can be explained mesoscale by the effect of surface tension on the melted binder, and
the homogenized effect of the surface tension is the so called sintering stress.
From the macroscopic perspective, the specimen (green body) shrinks due to this volumetric sintering stress. In the case of inhomogeneous
initial density in the green body, this procedure can result in unwanted deformations.

%Basis:
%Sintering, sintering stress, inhomogeneous shrinkage

Finite elements and computational homogenization have been applied to a Representative Volume Element (RVE) of the mesoscale.
The melted binder is modeled as a Stokes flow, with surface tension potential energy on the free surface. Hard inclusions are modeled by applying a high viscosity.
%This is coupled to the macroscopic stress and strain and the mesoscale  is solved for every time step in every integration point.
Different choices of boundary conditions are available on the RVE for the prolongation.
The advantage of this kind of approach is that it can capture the complex behavior of sintering with simple material models with measurable parameters.
%For the macro scale
%Method:
%Multi scale (FE$^2$, Homogenization)
%Macro scale: deformation.
%Micro scale: Stokes flow, surface tension.

%Examples, 
Numerical examples are evaluated for a 2D, fully coupled, FE$^2$ problem as a proof of concept.
Taylor-Hood elements for the linear Stokes flow, and quadratic edge elements for the surface tension, are employed for the mesoscale.
Dirichlet boundary conditions are used for the prolongation of the macroscopic strain rate.
Linear triangular elements with one integration point are used on the macroscopic scale.
This is shown for both with and without hard inclusions and a viscous melt subjected to surface tension.
The examples show how an inhomogeneous initial density will cause the macroscopic body to
undergo deformation
%shear
during the sintering process.
On the mesoscale, particles are merged, driven by the surface tension on the free pore surface.

}

\begin{document}
\maketitle
\end{document}

