\documentclass[a4paper,11pt]{article}
\usepackage[english]{babel}
\usepackage[margin=2.5cm,includehead,includefoot]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,contmech}
\usepackage[textsize=tiny,color=blue!10]{todonotes}

\usepackage{ifluatex}
\ifluatex
\renewcommand{\ta}[1]{\mathbfit{#1}}
\renewcommand{\ts}[1]{\mathbfit{#1}}
\renewcommand{\td}[1]{\mathbfcal{#1}}
\renewcommand{\tf}[1]{\mathbfsfup{#1}}
\renewcommand{\Box}{\mdlgwhtsquare}
\renewcommand{\leadsto}{\rightsquigarrow}

\usepackage{fontspec}
\usepackage{unicode-math}

\setmainfont[Ligatures=TeX]{xits}
\setmathfont[math-style=ISO]{xits-math}
%\setmainfont[Ligatures=TeX]{Latin Modern Roman}
%\setmathfont[math-style=ISO]{lmmath-regular.otf}
\else
\usepackage[utf8]{inputenc}
\fi

\usepackage{microtype}

% Extra commands;
\newcommand{\pressure}{\mathrm{p}}
\newcommand{\internal}{\mathrm{int}}
\newcommand{\external}{\mathrm{ext}}


\usepackage{fancyhdr}
\headheight=14.5pt
\pagestyle{fancy}
\fancyhead[r]{\today}
\fancyhead[l]{Mikael Öhman, Fredrik Larsson}

\newcommand{\ATS}{\bar{\tf E}}
\newcommand{\BC}{\mathrm{BC}}

\usepackage{enumitem}
\setlist[itemize]{itemindent=-1.5em}
\begin{document}
% Document composed after discussion with Fredrik on how to split to a mixed macroscale formulation.
% On the macro level:
%  \begin{gather}
%   -\bar{\ts\sigma}_\dev + \diff \bar p = \ta b\\
%   \diff\cdot \bar{\ta v} + \bar d_\vol = 0
%  \end{gather}
% 
% And the extension to the constitutive driver:
%  \begin{gather}
%   [\bar{\ts\sigma}_\dev, \bar{d}_\vol; \ATS_\dev] = f(\bar{\ts d}_\dev,\bar p)
%  \end{gather}
% 
% If dense RVE $\implies$
%  \begin{gather}
%   \bar d_\vol = 0\\
%   \ts d = \ts d_\dev \leadsto \bar{\ts\sigma}_\dev, \; \ATS_\dev
%  \end{gather}
% else
%  \begin{gather}
%   \bar d_\vol^{(0)} = 0\\
%   \bar{\ts d}^{(k)} = \bar{\ts d}_\dev + \frac13 \bar d_\vol^{(k)} \ts I\\
%   \bar p \approx \bar p^{(k)} + E_\eqv \Delta d_\vol\\
%   \bar d_\vol^{(k+1)} = \bar d_\vol^{(k)} - E_\eqv^{-1} (\bar p^{(k)} - \bar p)
%  \end{gather}
% 
% To perform Newton iterations the tangent $E_\eqv$ is needed;
%  \begin{gather}
%   \dif\bar{\ts\sigma} = \ATS \dprod \dif\bar{\ts d} \implies \\
%   \dif\bar{\ts\sigma}\dprod \ts I = \dif\bar{\ts\sigma}_\dev - \dif p \ts I \dprod \ts I 
%     = \ts I \dprod \ATS \dprod \dif \bar{\ts d}_\dev + \ts I \dprod \ATS \dprod \ts I \frac13 \dif \bar d_\vol \implies\\
%   \dif p = \underbrace{- \frac19\ts I \dprod \ATS \dprod \ts I}_{=E_\eqv} \dif \bar d_\vol 
%  \end{gather}
% 
% An possible alternative approach would be to mix the boundary conditions
%  \begin{gather}
%   \ta v = \bar{\ts d}_\dev\cdot(\ta x - \bar{\ta x}) + \frac13 \bar{d}_\vol (\ta x-\bar{\ta x})\text{ on } \Gamma_\Box \\
%   \ta t^+ = -(\bar{p}-\bar{p}_0) \ta n \text{ on } \Gamma_\Box
%  \end{gather}
% where $\bar d_\vol$ is unknown and $\bar{p}_0$ is the ``internal pressure'' (assuming no pores on the boundary)

%%%%%%%%%% NEW CONTENT %%%%%%%%%%%%%

\begin{center}
 \Large\bfseries On compressible/incompressible FE\textsuperscript{2} with application on liquid phase sintering.
\end{center}
\begin{abstract}
\noindent Prolongation and computational homogenization for is shown for mixed compressible\-/\-incompressible subscale behavior.
The macroscale formulation is separated into deviatoric strain rate and pressure,
with classical momentum balance and continuity equation including source term to deal with compressibility.
A nested, iterative approach, is shown for use with standard prolongation conditions.
A monolithic approach is also shown, where the volumetric strain rate, $\bar{d}_\vol$, is a primary unknown in the subscale FE-problem.
In particular the implementation for a monolithic Dirichlet type boundary condition is shown, including numerical examples.
\end{abstract}

\section{Introduction}
\begin{itemize}
 \item Something about computational homogenization and standard prolongation conditions. Suitable references to Geers and others.
\end{itemize}

Problems arise with standard prolongation conditions when the subscale behavior goes from compressible to incompressible, e.g.\ sintering or powder compaction.
In the case of liquid phase sintering, the subscale becomes completely or near incompressible when the porosity vanishes. 
Penalty methods can be used to deal with the changing subscale property, but yields unsatisfactory numerical properties and an additional source of error.
This paper proposes a new homogenization scheme to deal with these problems in a natural way.

The paper is structured as follows: 
The features of the macro scale problem (both incompressible and compressible flow) are presented in Section \ref{sec:macro}.
This is followed in Section \ref{sec:nested} which deals with the nested formulation for the RVE problem, 
where the compressible and incompressible case are presented in Section \ref{sec:nested_compressible} and \ref{sec:nested_incompressible} respectively.
The monolithic formulation is presented in Section \ref{sec:monolithic}. Section \ref{sec:numerical_examples} shows some numerical examples.
Conclusions and an outlook to future developments are given in the final section.

\section{Preliminaries and Notation}\label{sec:preliminaries}
The use of an over-bar, $\bar{\bullet}$, refers to a homogenized, macroscopic, quantity, while the subscript box, $\bar{\bullet}_\Box$, refers to the homogenized quantity of a Representative Volume Element (RVE). Brackets and parenthesis are used to denote implicit and explicit functions respectively.

An important part of the theory is the

\section{The macro-scale problem} \label{sec:macro}
Consider the macroscale problem at quasistatic equilibrium, stated as
\begin{align}
 -\bar{\ts\sigma}\cdot \diff = \bar{\ts b} \quad \text{in } \Omega
\end{align}
where we seek the macroscale velocity $\bar{\ts v}$. In particular, we identify two possible responses (induced by the submodel presented below):
\begin{gather}
 \bar{\ts\sigma} = \bar{\ts\sigma}_\Box\{\bar{\ts d}\} \label{eq:macro_compressible}
\end{gather}
\vspace{-2\baselineskip} % Why do i need this? Caused by subequations.
\begin{subequations} \label{eq:macro_incompressible}
\begin{align}
  \bar{\ts\sigma} = \bar{\ts\sigma}_{\Box,\dev}\{\bar{\ts d}_\dev, \bar p\} - \bar p \ts I\\
  \bar{d}_\vol = 0
\end{align}
\end{subequations}
where \eqref{eq:macro_compressible} pertains to compressible and \eqref{eq:macro_incompressible} to incompressible response.
In order to comply with both cases, we generalize the formulation as follows:
\begin{subequations} \label{eq:macro_mixed}
\begin{gather}
 \bar{\ts\sigma} = \bar{\ts\sigma}_{\Box,\dev}\{\bar{\ts d}_\dev,\bar p\} - \bar p\ts I\\
 \bar{d}_\vol - \bar{d}_{\Box,\vol}\{\bar{\ts d}_\dev, \bar p\} = 0
\end{gather}
\end{subequations}
Here we introduced $\bar{\ts d} = \left[ \bar{\ta v} \outerp \diff \right]^\sym$, $\bar{d}_\vol = \ts I \dprod \bar{\ts d}$ and $\bar{\ts d}_\dev = \bar{\ts d} - \frac{\bar d_\vol}{3}\ts I$ 

We shall now show that the formulation in \eqref{eq:macro_mixed} comprises both cases in \eqref{eq:macro_compressible} and \eqref{eq:macro_incompressible}
First we note that \eqref{eq:macro_incompressible} is trivially identified by 
\begin{align}
 \bar{\ts\sigma}_{\Box,\dev}\{\bar{\ts d}_\dev, \bar p\}, \quad \bar{d}_{\Box,\vol}\{\bar{\ts d}_\dev,\bar p\} = 0
\end{align}
Equation \eqref{eq:macro_compressible} can be recast into \eqref{eq:macro_mixed} by defining
\begin{align}
 \bar d_{\Box,\vol}\{\bar{\ts d}_\dev, \bar p\} = \bar{d}_\vol^*,\quad \text{s.t. } -\frac13 \ts I\dprod \bar{\ts\sigma}_\Box\{\bar{\ts d}_\dev +\frac13\bar{d}_\vol^*\ts I\} = \bar p.
\end{align}
Consequently, the deviatoric stress is defined as
\begin{align}
 \bar{\ts\sigma}_{\Box,\dev}\{\bar{\ts d}_\dev,\bar p\} = \tf I_\dev \dprod \bar{\ts\sigma}_\Box\{\bar{\ts d}_\dev + \frac13 \bar{d}_\vol^*\ts I\}.
\end{align}

\subsection{Macro-scale problem}
Starting from the formulation in \eqref{eq:macro_mixed} we state the mean form as that of finding $(\bar{\ta v},\bar p) \in \bar{\set V} \times \bar{\set{P}}$ s.t.
\todo{Why brackets on all of these?}
\begin{align}
 \bar a\{\bar{\ta v},\bar p; \delta\bar{\ta v}\} - \bar b\{\bar p, \delta\bar{\ta v}\} &= \bar{l}\{\delta\bar{\ta v}\}   \quad \forall\; \delta\bar{\ta v} \in \bar{\set{V}}^0\\
 \bar b\{\delta\bar p, \bar{\ta v}\} - \bar c\{\bar{\ta v}, \bar p; \delta\bar p\}&= 0   \quad \forall\; \delta\bar p \in \bar{\set{P}}
\end{align}
in the weak form above, we defined
\begin{align}
 \bar a\{\bar{\ta v},\bar p; \delta\bar{\ta v}\} &\defeq \int_\Omega \bar{\ts\sigma}_{\Box,\dev}\{[\bar{\ta v}\outerp \diff]^\sym_\dev,\bar p\}\dprod [\delta\bar{\ta v}\outerp \diff]^\sym_\dev \dif V \\
 \bar b\{\bar p, \delta\bar{\ta v}\}             &\defeq \int_\Omega \bar p[\delta\bar{\ta v}\cdot\diff]\dif V \\
 \bar c\{\bar{\ta v}, \bar p; \delta\bar p\}     &\defeq \int_\Omega \bar d_{\Box,\vol}\{[\bar{\ta v}\outerp \diff]^\sym_\dev,\bar p\}\delta\bar p\dif V
\end{align}
Newton iterations are obtained as
\begin{align}
 \bar{a}'_p\{\bullet; \delta\bar{\ta v},\Delta\bar{p}\} + \bar{a}'_v\{\bullet; \delta\bar{\ta v},\Delta\bar{\ta v}\} - \bar{b}\{\Delta\bar p, \delta{\ta v}\}
	  &= -\bar{a}\{\bullet; \delta\bar{\ta v}\} + \bar{b}\{\bullet, \delta\bar{\ta v}\} + \bar{l}\{\delta\bar{\ta v}\} \quad &&\forall \delta\bar{\ta v}\in \bar{\set{V}}^0\\
%
\bar{b}\{\delta\bar p, \Delta\bar{\ta v}\} - \bar{c}'_v\{\bullet; \delta\bar{p}, \Delta\bar{ \ta v}\} - \bar{c}'_p\{\bullet; \delta\bar{p},\Delta\bar{p}\}
	  &= -\bar{b}\{\delta\bar{p},\bullet\} + \bar{c}\{\bullet;\delta\bar{p}\}\quad &&\forall \delta\bar{p} \in \bar{\set{P}}
\end{align}
where
\begin{align}
 \bar{a}'_v\{\bullet; \delta\bar{\ta v},\Delta\bar{\ta v}\} &= \int_\Omega [\delta\bar{\ta v}\outerp\diff]^\sym_\dev \dprod \pd{\bar{\ts\sigma}_{\Box,\dev}}{\bar{\ts d}_\dev} \dprod [\Delta\bar{\ta v}\outerp\diff]^\sym_\dev \dif V\\
 \bar{a}'_p\{\bullet; \delta\bar{\ta v},\Delta\bar{p}\}     &= \int_\Omega [\delta\bar{\ta v}\outerp\diff]^\sym_\dev \dprod \pd{\bar{\ts\sigma}_{\Box,\dev}}{\bar{p}} \Delta\bar{p} \dif V\\
 \bar{c}'_v\{\bullet; \delta\bar{p}, \Delta\bar{ \ta v}\}   &= \int_\Omega \delta\bar{p} \pd{\bar{d}_{\Box,\vol}}{\bar{\ts d}_\dev} \dprod [\Delta\bar{\ta v}\outerp\diff]^\sym_\dev \dif V\\
 \bar{c}'_p\{\bullet; \delta\bar{p},\Delta\bar{p}\}         &= \int_\Omega \delta\bar{p} \pd{\bar{d}_{\Box,\vol}}{\bar p} \Delta\bar p\dif V
\end{align}

\section{Nested analysis}  \label{sec:nested}
Assuming that the subscale problem is stated either as that of \eqref{eq:macro_compressible} or \eqref{eq:macro_incompressible} respectively we need to treat the two cases separately.
Worth noting is that the subscale problem can shift from one case to another during an analysis, e.g. compaction of porous media or liquid phase sintering.
\todo{Cite and refer to problems in paper A}

\subsection{Compressible subproblem} \label{sec:nested_compressible}
We assume that the subscale problem defines the function 
\begin{align}
 \bar{\ts\sigma} = \bar{\ts\sigma}_\Box\{\bar{\ts d}\}\quad \text{and its derivative } \bar{\tf E} = \od{\bar{\ts\sigma}_\Box}{\bar{\ts d}}.
\end{align}
In order to utilize the general formulation in \eqref{eq:macro_mixed}, we formulate the intermediate problem of finding $\bar{d}_\vol^*$ s.t.
\begin{align} \label{eq:find_pressure}
 \frac13 \ts I\dprod \bar{\ts\sigma}_\Box\{\bar{\ts d}_\dev + \frac13 \bar{d}_\vol^* \ts I\} = -\bar p.
\end{align}
The iterative solution can be obtained by the update
\begin{align}
 \Delta\bar{d}_\vol &= \frac{1}{\bar K(\bar{\ts d}^{(k)})} \left[-\bar p - \frac13 \ts I\dprod \bar{\ts\sigma}_\Box\{\bar{\ts d}^{(k)}\}\right] \quad \text{with}\quad \bar{\ts d}^{(k)} = \bar{\ts d}_\dev + \frac13 \bar{d}_\vol^{(k)} \ts I\\
 \bar{d}_\vol^{(k+1)} &= \bar{d}_\vol^{(k)} + \Delta\bar{d}_\vol
\end{align}
Here, we introduced the bulk stiffness
\begin{align}
  \bar K\{\bar{\ts d}\} \defeq \frac19  \ts I\dprod \bar{\tf E} \dprod \ts I.
\end{align}
Finally, we state the equations pertinent to \eqref{eq:macro_mixed} as follows
\begin{align}
 \left\{ \begin{aligned}
         \bar{\ts\sigma}_{\Box,\dev} &= \tf I_\dev \dprod \bar{\ts\sigma}_\Box\{\bar{\ts d}_\dev + \frac13 \bar{d}_\vol^* \ts I\}\\
         \bar{d}_{\Box,\vol} &= \bar{d}_\vol^*
        \end{aligned}
 \right.
\end{align}
Pertubations of the input, i.e. $\bar{\ts d}_\dev$ and $\bar p$,  give rise to the pertinent output pertubations:
\begin{align}
 \dif\bar{\ts\sigma}_{\Box,\dev} &= \tf I_\dev \dprod \dif\bar{\ts\sigma} = \tf I_\dev \dprod \dif\bar{\ts\sigma} = \tf I_\dev \dprod \bar{\tf E} \dprod \left[\dif\bar{\ts d}_\dev + \frac13 \ts I \dif\bar{d}_\vol\right]\\
	  &= \tf I_\dev \dprod \bar{\tf E} \dprod \left[\tf I + \frac13 \ts I\outerp \od{\bar{d}_\vol^*}{\bar{\ts d}_\dev} \right] \dprod \dif\bar{\ts d}_\dev + \frac13 \tf I_\dev \dprod \bar{\tf E}\dprod \ts I \od{\bar{d}_\vol^*}{\bar p}\dif\bar{p}\\
 \dif\bar{d}_{\Box,\vol} &= \od{\bar{d}_\vol^*}{\bar{\ts d}_\dev}\dprod \dif \bar{\ts d}_\dev + \od{\bar{\ts d}_\vol}{\bar p}\dif \bar p
\end{align}
where the sensitivities are derived from the linearization of \eqref{eq:find_pressure} as
\begin{align}
 \frac19 \ts I\dprod \bar{\tf E} \dprod \ts I\outerp \od{\bar{d}_\vol^*}{\bar{\ts d}_\dev} &= -\frac13 \ts I\dprod \bar{\tf E} 
	\implies \od{\bar{d}_\vol^*}{\bar{\ts d}_\dev} = - \frac1{3\bar{K}} \ts I\dprod \bar{\tf E}\\
 \frac19 \ts I\dprod \bar{\tf E} \dprod \ts I\od{\bar d_\vol^*}{\bar p} &= -1
	\implies \od{\bar{d}_\vol^*}{\bar{p}} = -\frac{1}{\bar{K}}
\end{align}


Finally we can thus state 
\begin{align}
 \pd{\bar{\ts\sigma}_{\Box,\dev}}{\bar{\ts d}_\dev} &= \tf I_\dev \dprod \left[ \bar{\tf E} - \frac1{9\bar K} \bar{\tf E}\dprod \ts I\outerp \bar{\tf E}\outerp\ts I\right]\\
 \pd{\bar{\ts\sigma}_{\Box,\dev}}{\bar{p}} &= -\frac1{3\bar{K}} \tf I_\dev \dprod \bar{\tf E}\dprod \ts I\\
 \pd{\bar d_{\Box,\vol}}{\bar{\ts d}_\dev} &= -\frac1{3\bar{K}} \ts I\dprod \bar{\tf E}\\
 \pd{\bar d_{\Box,\vol}}{\bar{p}} &= -\frac1{\bar{K}}
\end{align}

\subsection{Incompressible subproblem} \label{sec:nested_incompressible}
If the subscale is, or becomes, incompressible a different approach is needed.
An incompressible subproblem is defined by forcing $\bar{d}_\vol\{\ts d_\dev,\bar{p}\} = 0$, with the corresponding tangent $\frac{1}{\bar{K}} = 0$.
This can be detected by computing the porosity.\todo{Refer to paper A}
The subscale problem is
\begin{align}
 a_\Box(\ta v; \delta\ta v) - b_\Box(p,\delta\ta v) &= 0\quad \forall\;\delta\ta v \in \set V^0 \\
 b_\Box(\delta p, \ta v) &= 0\quad \forall\;\delta p \in \set P\setminus\set R
\end{align}
where we have assumed that the subscale fields do not depend on absolute value of the pressure; $\ta v = \ta v(\bar{\ts d}_\dev)$ and $p = p(\bar{\ts d}_\dev)$.
Standard Dirichlet, Neumann \todo{Does it come naturally for Neumann bc already?} or microperiodic boundary conditions for the deviatoric strain rate can be applied.
For these boundary conditions combined with the case that the microstructure doesn't have any free surfaces, 
the pressure needs to be set at some point to make the system solvable.

If the the subscale constitutive behavior directly depends on the pressure $p$, an approach like that in Section \ref{sec:monolithic} is required.
\todo{More on this section later...}

\section{Monolithic formulation} \label{sec:monolithic}
The general problem for subscale flow can be written as
\begin{align}
 \underbrace{\frac{1}{|\Omega_\Box|} \int_{\Omega_\Box} \ts\sigma(\ta v, p)\dprod [\delta\ta v\outerp\diff] \dif V}_{a_\Box(\ta v,p;\delta\ta v^\fluct)-b_\Box(p,\delta\ta v^\fluct)}
	= \underbrace{\frac{1}{|\Omega_\Box|} \int_{\Gamma_\Box^\external \cup \Gamma_\Box^\internal} \ta t\cdot \delta\ta v\dif S}_{l_\Box^\external(\delta\ta v^\fluct)+l_\Box^\internal(\delta \ta v^\fluct)}
 \label{eq:subscale_original}
\end{align}
where $l_\Box^\external$ is the reaction force.
\subsection{Dirichlet boundary condition}
The velocity is split into
\begin{align}
 \ta v = \ta v^\macro + \ta v^\fluct = \bar{\ts d}_\dev \cdot \ta x^\macro + \bar{d}_\vol \ta x_\vol^\macro + \ta v^\fluct.
\end{align}
where
\begin{align}
 \ta x^\macro \defeq& [\ta x - \bar{\ta x}]\phantom{\frac13} \quad\text{on } \Gamma_\Box^\external
 \label{eq:basefunction}
\\
\ta x_\vol^\macro \defeq & \frac13[\ta x - \bar{\ta x}] \quad\text{on } \Gamma_\Box^\external
 \label{eq:basefunction_vol}
\end{align}
 
For the additional unknown, $\bar{d}_\vol$, we choose the corresponding test function $\delta[\bar{d}_\vol \ta x_\vol^\macro] = \delta\bar{d}_\vol\ta x_\vol^\macro$.
Introducing $\delta[\bar{d}_\vol \ta x_\vol^\macro]$, $\delta p$ and $\delta\ta v$ in \eqref{eq:subscale_original}, the subscale problem can be expressed as finding $(\ta v, p,\bar{d}_\vol) \in \set{V}_\Box^0 \times \set{P}_\Box \times \set{R}$ in
\begin{align}
 \label{eq:v_equation}&a_\Box \left(\ta v, p; \delta\ta v \right) -b_\Box \left(p,\delta\ta v\right) &&= l_\Box^\internal\left(\delta\ta v\right) &&\forall\:\delta\ta v \in \set{V}_\Box^0\\
 \label{eq:p_equation}&b_\Box\left(\delta p, \ta v\right) &&= 0 &&\forall\: \delta p \in \set{P}_\Box\\
 \label{eq:d_equation}&\left[a_\Box\left(\ta v, p; \ta x_\vol^\macro\right)- b_\Box\left(p,\ta x_\vol^\macro\right)\right]\delta\bar{d}_\vol &&= [-\bar p+l_\Box^\internal(\ta x^\macro_\vol)]\delta\bar{d}_\vol &&\forall\: \delta\bar{d}_\vol \in \set{R}
\end{align}
where, as with standard Dirichlet boundary condition, $\ta v^\fluct = 0$ on $\Gamma_\Box$.
In \eqref{eq:d_equation} we recognize the homogenized pressure from 
\begin{align}
 l_\Box^\external(\ta x^\macro_\vol) = \frac13\int_{\Gamma_\Box^\external} \ta t \cdot [\ta x - \bar{\ta x}]\dif S = -\bar{p}.
\end{align}

The particular choice in \eqref{eq:basefunction} and \eqref{eq:basefunction_vol} means that the boundary condition is localized on $\Gamma_\Box^\external$. For the internal velocity field the total velocity is solved for directly.
% where we define $\ta v_\vol \defeq -\frac13[\ta x - \bar{\ta x}]$ and used, for brevity
% \begin{align}
%  \ta v = \bar{\ts d}_\dev \cdot [\ta x - \bar{\ta x}] - \bar{d}_\vol \ta v_\vol + \ta v^\fluct.
% \end{align}

The output (for given $\bar{\ts d}_\dev$, $\bar p$) is $\bar{d}_{\Box,\vol}\{\bar{\ts d}_\dev,\bar p\} = \bar{d}_\vol$,
which is solved for directly, and the post processed deviatoric stress which is obtained from computational homogenization
\begin{align}
 \bar{\ts\sigma} &= \frac{1}{|\Omega_\Box|} \int_{\Gamma_\Box^\external} \ta t\outerp[\ta x -\bar{\ta x}]\dif S \\
 \nonumber \implies (\bar{\ts\sigma})_{ij} &= \frac{1}{|\Omega_\Box|} \int_{\Gamma_\Box^\external} (\ta t)_i ([\ta x -\bar{\ta x}])_j\dif S
  \\ &= \frac{1}{|\Omega_\Box|} \int_{\Gamma_\Box^\external} \ta t \cdot \be i \outerp \be j \cdot [\ta x -\bar{\ta x}]\dif S = l_\Box^\external(\underbrace{\be i \outerp \be j \cdot \ta x^\macro}_{\ta v^{\macro(ij)}})\\
 \bar{p} &= -l_\Box^\external(\ta x^\macro_\vol)\\
 \implies (\bar{\ts\sigma}_\dev)_{ij} &= (\bar{\ts\sigma})_{ij} + \delta_{ij} \bar{p} = l_\Box^\external(\underbrace{\ta v^{\macro(ij)} -\delta_{ij} \ta x_\vol^\macro}_{\ta v_\dev^{\macro(ij)}})
%  \bar{\ts\sigma}_{\Box,\dev}(\bar{\ts d}_\dev,\bar p)
%   &=\sum_{ij} \left[ a_\Box\left(\ta v, p; \ta v^{\macro\dev(ij)}\right) - \underbrace{b_\Box\left(p,\ta v^{\macro\dev(ij)}\right)}_{=0} - l_\Box^\internal\left(\ta v^{\macro\dev(ij)}\right)\right] \bee ij
\end{align}
% \subsection{Dirichlet boundary condition} \label{sec:monolithic_dirichlet}
% As with standard Dirichlet boundary conditions for computational homogenization, we simply choose $\delta\ta v^\fluct = \ta 0$ on $\Gamma_\Box$.

% \subsection{Neumann boundary condition} \label{sec:monolithic_neumann}
% Similar to the standard Neumann boundary condition we apply $\ta t = \bar{\ts\sigma} = -\bar{p}\ta n + \bar{\ts\sigma}_\dev$.

\subsubsection{Sensitivity analysis}
\todo{This section is under heavy construction}
For brevity, the following notation is introduced
\begin{align}
 v_\Box(\Delta\ta v,\Delta p) &= a_{\Box,v}'(\bullet; \delta\ta v, \Delta\ta v) + a_{\Box,p}'(\bullet; \delta\ta v,\Delta p) - b_\Box(\Delta p,\delta\ta v)\\
 d_\Box(\Delta\ta v,\Delta p) &= a_{\Box,v}'(\bullet; \delta\bar{d}_\vol\ta x^\macro_\vol,\Delta\ta v) + a_{\Box,p}'(\bullet;\delta\bar{d}_\vol\ta x^\macro_\vol,\Delta\ta v) - b_\Box(\Delta p,\delta\bar{d}_\vol\ta x^\macro_\vol)
\end{align}

Primal sensitivity
% \begin{align}
%  &a_{\Box,v}'(\bullet; \delta\ta v, \Delta\ta v) + a_{\Box,p}'(\bullet; \delta\ta v,\Delta p) - b_\Box(\Delta p,\delta\ta v) = 0 && \forall\; \delta\ta v\in \set{V}_\Box^0\\
%  &b_\Box(\delta p,\Delta\ta v) + b_\Box(\delta p,\ta x^\macro_\vol) \Delta\bar{d}_\vol = 0 && \forall\; \delta p \in \set{P}_\Box\\
%  \nonumber &[a_{\Box,v}'(\bullet; \ta x^\macro_\vol,\Delta\ta v) + a_{\Box,v}'(\bullet;\ta x^\macro_\vol,\ta x^\macro_\vol)\Delta\bar{d}_\vol\\
%   &+a_{\Box,p}'(\bullet;\ta x^\macro_\vol,\Delta p) - b_\Box(\Delta p,\ta x^\macro_\vol)]\delta\bar{d}_\vol
% 	= -\Delta\bar{p} \delta\bar{d}_\vol && \forall\;\delta\bar{d}_\vol \in \set{R}
% \end{align}
\begin{align}
 &v_\Box(\Delta\ta v,\Delta p) = 0 && \forall\; \delta\ta v\in \set{V}_\Box^0\\
 &b_\Box(\delta p,\Delta\ta v) + b_\Box(\delta p,\ta x^\macro_\vol) \Delta\bar{d}_\vol = 0 && \forall\; \delta p \in \set{P}_\Box\\
 &d_\Box(\Delta\ta v,\Delta p) = -\Delta\bar{p} \delta\bar{d}_\vol && \forall\;\delta\bar{d}_\vol \in \set{R}
\end{align}

Super position
\begin{align}
 \Delta \ta v^\dev = \sum_{ij} \hat{\ta v}^{\Delta(ij)} \Delta(\bar{\ts d}_\dev)_{ij} + \hat{v}^p \Delta\bar{p}
 \\
 \Delta \bar{d}_\vol = \sum_{ij} \hat{d}^{\Delta(ij)} \Delta(\bar{\ts d}_\dev)_{ij} + \hat{d}^p \Delta\bar{p}
 \\
 \Delta p = \sum_{ij} \hat{p}^{\Delta(ij)} \Delta(\bar{\ts d}_\dev)_{ij} + \hat{p}^p \Delta\bar{p}
\end{align}

Sensitivity in $(\bar{\ts d}_\dev)_{ij}$: $(\hat{\ta v}^{\Delta(ij)}, \hat{p}^{\Delta(ij)}, \hat{d}^{\Delta(ij)}) \in \set{V}_\Box(\be i\outerp\be j - \frac13\be i\cdot\be j\ts I)\times \set{P}_\Box \times\set{R}$
\begin{align}
 &v_\Box(\hat{\ta v}^{\Delta(ij)}+\ta x^\macro_\vol \hat{d}^{\Delta(ij)}, \hat{p}^{\Delta(ij)}) = 0
 %&a_{\Box,v}'(\bullet;\delta\ta v, )+a_{\Box,p}'(\bullet;\delta\ta v,\hat{p}^{\Delta(ij)}) - b_\Box(\hat{p}^{\Delta(ij)},\delta\ta v) = 0
 \\
 &b_\Box(\delta p,\hat{\ta v}^{\Delta(ij)} + \ta x^\macro_\vol \hat{d}^{\Delta(ij)}) = 0
 \\
 &d_\Box(\delta\bar{d}_\vol\ta x^\macro_\vol,\hat{\ta v}^{\Delta(ij)}+\ta x^\macro_\vol \hat{d}^{\Delta(ij)}) = 0
 %&\delta\bar{d}_\vol[a_{\Box,v}'(\bullet; \ta x^\macro_\vol, \hat{\ta v}^{\Delta(ij)}+\ta x^\macro_\vol \hat{d}^{\Delta(ij)}) + a_{\Box,p}'(\bullet;\ta x^\macro_\vol,\hat{p}^{\Delta(ij)}) - b_\Box(\hat{p}^{\Delta(ij)},\ta x^\macro_\vol)] = 0
\end{align}

Sensitivity in $\bar p$: $(\hat{\ta v}^{p}, \hat{p}^{p}, \hat{d}^{p}) \in \set{V}_\Box(0)\times \set{P}_\Box \times\set{R}$
\begin{align}
 &v_\Box(\delta\ta v, \hat{\ta v}^{p}+\ta x^\macro_\vol \hat{d}^{p}) = 0
 %&a_{\Box,v}'(\bullet;\delta\ta v, \hat{\ta v}^{p}+\ta x^\macro_\vol \hat{d}^{p})+a_{\Box,p}'(\bullet;\delta\ta v,\hat{p}^{p}) - b_\Box(\hat{p}^{p},\delta\ta v) = 0
 \\
 &b_\Box(\delta p,\hat{\ta v}^{p} + \ta x^\macro_\vol \hat{d}^{p}) = 0
 \\
 &d_\Box(\delta\bar{d}_\vol \ta x^\macro_\vol, \hat{\ta v}^{p}+\ta x^\macro_\vol \hat{d}^{p}) = 0
 %&\delta\bar{d}_\vol[a_{\Box,v}'(\bullet; \ta x^\macro_\vol, \hat{\ta v}^{p}+\ta x^\macro_\vol \hat{d}^{p}) + a_{\Box,p}'(\bullet;\ta x^\macro_\vol,\hat{p}^{p}) - b_\Box(\hat{p}^{p},\ta x^\macro_\vol)] = -1 \delta\bar{d}_\vol
\end{align}

Expansion of $\Delta\bar{d}_\vol$
\begin{align}
 \nonumber \Delta\bar{d}_\vol &= \sum_{ij} \hat{d}^{\Delta(ij)} \Delta(\bar{\ts d}_\dev)_{ij} + \hat{d}^p\Delta\bar{p}\\
 &= \left(\sum_{ij} \hat{d}^{\Delta(ij)} \be i\outerp \be j\right) \dprod \Delta\bar{d}_\dev + \hat{d}^p \Delta\bar{p}
\end{align}

Linearization of $\bar{\ts\sigma}_\dev$
\begin{align}
 \Delta(\bar{\ts\sigma}_\dev)_{ij} = v(\ta v^{\macro\dev(ij)}, \Delta\ta v) 
\end{align}


\begin{align}
  \Delta\bar{\ts\sigma}_\dev &= \sum_{ij} \hat{d}^{\Delta(ij)} \Delta(\bar{\ts\sigma}_\dev)_{ij}
\end{align}

\subsection{Neumann boundary condition}
In comparison with Dirichlet boundary condition, modification to the classical Neumann boundary condition is simple to implement.
The split is not introduced in the external, unknown, traction as
\begin{align}
 \ta t = \bar{\ts\sigma}\cdot\ta n = \bar{\ts\sigma}_\dev\cdot\ta n + \bar p \ta n = \sum_i \bar{\sigma}_{\dev,i} \ts E_i\cdot \ta n + \bar p \ta n \quad \text{on }\Gamma_\Box
\end{align}


\subsubsection{Sensitivity analysis}

\subsection{Microperiodic boundary condition}
\subsubsection{Sensitivity analysis}

% \subsection{Weakly microperiodic boundary condition}
% \subsubsection{Sensitivity analysis}

% \begin{align}
%  \pd{\bar{\ts\sigma}_\dev}{\bar{\ts d}_\dev} &= \\
%  \pd{\bar{\ts\sigma}_\dev}{\bar p} &= \\
%  \pd{\bar{d}_\vol}{\bar{\ts d}_\dev} &= \\
%  \pd{\bar{d}_\vol}{\bar p} &=
% \end{align}

\section{Conclusions and outlook} \label{sec:conclusions}

\end{document}
